%-------------------------
% Resume in Latex
% Author : Naeem
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------


\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}
\usepackage{lastpage}                       % Page numbering
\usepackage{fancyhdr}                       % Footers
\usepackage[usenames,dvipsnames]{xcolor}    % Coloring

%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}

\usepackage[autostyle,english=american]{csquotes}
\MakeOuterQuote{"}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

%Footer
\fancyfoot[C]{Page \thepage \hspace{1pt} of \pageref{LastPage}}

%Text Color

\def\theme{MidnightBlue}
\definecolor{color-text}{gray}{0.10}    % light black
\definecolor{color-detail}{gray}{0.40}  % dark gray
\colorlet{color-title}{\theme}          % black

% Set text color
\makeatletter
\newcommand{\globalcolor}[1]{\color{#1}\global\let\default@color\current@color}
\makeatother
\AtBeginDocument{\globalcolor{color-text}}


% Adjust margins
\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}
% Sections formatting

%\titleformat{\section}{
%  \vspace{-4pt}\scshape\raggedright\large\color{color-title}
%}{}{0em}{}[\color{color-title}\titlerule \vspace{-5pt}]

\titleformat{\section}{
   \vspace{-4pt} \scshape\raggedright\Large
    }{}{0em}{}[\titlerule
    \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textbf{\small #2} \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}


%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%----------HEADING----------
% \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
%   \textbf{\href{http://sourabhbajaj.com/}{\Large Sourabh Bajaj}} & Email : \href{mailto:sourabh@sourabhbajaj.com}{sourabh@sourabhbajaj.com}\\
%   \href{http://sourabhbajaj.com/}{http://www.sourabhbajaj.com} & Mobile : +1-123-456-7890 \\
% \end{tabular*}

\begin{center}
    {\Huge \scshape  Naeem Patel} \\ \vspace{1pt}
     Navi Mumbai \\ \vspace{1pt}
    \normalsize \raisebox{-0.1\height}\faPhone\ +91-9167139763 ~ \href{https://www.linkedin.com/in/naeem-010/}{\raisebox{-0.2\height}\faLinkedin\ \underline{linkedin.com/in/naeem-010}}  ~
    \href{https://github.com/Naeempatel010}{\raisebox{-0.2\height}\faGithub\ \underline{github.com/Naeempatel010}}
    \vspace{-8pt}
\end{center}


%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    
    \resumeSubheading
      {Fr. Conceicao Rodrigues Institute of Technology, Mumbai}{May 2020}
      {Secured a Bachelor of Computer Engineering with CGPA \textbf{9.26/10} }{}
    \resumeSubheading
      {DAV Public School, Nerul}{June 2016}
      {Secured  \textbf{94.8\%} in Higher Secondary Certificate Examination  \textbf{Gold Medal in Computer Science}}{}

  \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Tata Consultancy Services}{Aug 2020 -- Present}
      {System Engineer}{Mumbai, India}
      \resumeItemListStart
        \resumeItem{Coordinating with the foundation team for data virtualization, SAML integration and on-premise file storage.}
        \resumeItem{Developed a native intelligent workflow orchestration tool along a video streaming support using Spring Java.}
        \resumeItem{Responsible for onboarding machine learning task like anomaly detection, clustering algorithms, market research and customer segmentation.}
        \resumeItem{Creating ontologies for formal development of domain knowledge using interactive interface called wizard.}
      \resumeItemListEnd

    \resumeSubheading
      {Tata Institute of Fundamental Research}{May 2019 -- May 2020}
      {Project Intern}{Mumbai, India}
      \resumeItemListStart
        \resumeItem{Designed a custom YOLO architecture for detecting objects like ships and person as part of the surveillance system using C++, Qt and OpenCV library.}
        \resumeItem{Programmed the system to aid any person with no technical knowledge create complex deep learning models. Implemented annotation tool, Dataset splitting, Training using Darknet project and testing.}
    \resumeItemListEnd
    
    \resumeSubheading
      {Myraa Technologies}{May 2018 -- May 2019}
      {M-Visionary Researcher}{Navi Mumbai, India}
      \resumeItemListStart
        \resumeItem{Created an automated question generation from images/text for the Quiz application in the entertainment domain using Stanford’s CoreNLP Dependency parsers to extract Subject-verb-object. }
        \resumeItem{Developed a web application to exhibit the final end-to-end system using image as input, converted it into a caption, feed it into the question generation model to create questions and finally using unsupervised learning algorithm called gloVe to create similar looking options.}
        \resumeItem{Awarded \textbf{1st Rank} in the \textbf{FCRIT Incubation Center.}}

     \resumeItemListEnd
   \resumeSubheading
      {Cisco ThinQbator}{June 2020 -- July 2020}
      {Intern}{Mumbai, India}
      \resumeItemListStart
        \resumeItem{Developed a face recognition system for criminal tracking from CCTV footages. It is based on the FaceNet architecture and incorporates super resolution for improving the image quality and MTCNN for face detection.}
        \resumeItem{Demonstrated a robust prototype which is capable of recognizing images in low quality as well as requires very less re-training time for scaling the number of recognized faces.}
        \resumeItem{Won the \textbf{Most Feasible solution} award amongst more than \textbf{25 Teams}.}
     \resumeItemListEnd
\resumeItemListEnd
    
\vspace{-10pt}

%-----------PROJECTS-----------
\section{Projects}
    \resumeSubHeadingListStart
    \resumeProjectHeading
          {\textbf{Car Damage Detection using Mask R-CNN} $|$ \emph{Android Studio, Python, Web Technologies}}{March 2019}
          \resumeItemListStart
            \resumeItem{Devised a mobile application which can automatically detect damages in vehicle and semantically segment every minute crack using Mask R-CNN, a deep learning-based technique for semantic segmentation.}
            \resumeItem{Won the \textbf{winner} of the \textbf{Smart India Hackathon (SIH)2019} organized by HRD ministry of India and was amongst more than \textbf{1,00,000 participants} in 28 centers in the process were awarded a cash prize of \textbf{100,000 INR} by Ericsson.}
          \resumeItemListEnd
          \vspace{-10pt}
        \resumeProjectHeading
          {\textbf{WorkX – Platform for ideation, investment, creation and job seeking} $|$ \emph{Laravel}}{October 2019}
          \resumeItemListStart
            \resumeItem{Developed a platform for rural employment, wherein we proposed a platform through which a user can suggest ideas for startups, pick up startup ideas, request funding for those ideas as well as find people to work at these startups}
            \resumeItem{Selected as the \textbf{top 5} solutions from across the country for \textbf{final round of Manipal Hackathon} held in Karnataka wherein more than \textbf{400 solutions} were submitted.}
          \resumeItemListEnd
          \newpage
          \resumeProjectHeading
          {\textbf{Doctify - Personal medical Assistant} $|$ \emph{Laravel}}{April 2019}
          \resumeItemListStart
            \resumeItem{Developed a web application which can help in analyzing medical scans for brain haemorrhage, Pnemonia, Diabetes and Cancer}
            \resumeItem{Utilized Deep learning techniques like Convolutional Neural Network(CNN) trained on the freely available medical datasets on Kaggle.}
            \resumeItem{Selected as the \textbf{Top 25} project at the \textbf{Mumbai Hackathon 2019 amongst more than 200 entries}}
          \resumeItemListEnd
          \vspace{-12pt}
      \resumeProjectHeading
          {\textbf{Facial Emotion Detector } $|$ \emph{Python, OpenCV Library}}{July 2018}
          \resumeItemListStart
            \resumeItem{Developed an application to detect seven emotions (happy, sad, surprised, neutral, disgust, fear, angry) in real-time by using Haar cascade for face detection and a deep learning-based CNN model for emotion Detection.}
            \resumeItem{Awarded the \textbf{1st prize} in \textbf{CSI Summer Project Competition 2018}}
           \resumeItemListEnd
           \vspace{-15pt}
    \resumeProjectHeading
          {\textbf{JoJoTorrent - Peer-to-peer video streaming using Torrent} $|$ \emph{NodeJS}}{Sep 2020}
          \resumeItemListStart
            \resumeItem{Developed a peer-to-peer video streaming implementing the torrent protocol in order to stream large videos without any buffering.}
            \resumeItem{Enables streaming of videos over the browser using the WebRTC project eliminating the need to install plugins or download native apps.}
              \resumeItemListEnd
    \resumeSubHeadingListEnd

%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{:  C, C++, Java, Python, JavaScript, SQL} \\
     \textbf{Developer Tools}{: Eclipse, Azure Cloud} \\
     \textbf{Technologies/Frameworks}{: Spring, NodeJS, ReactJS, TensorFlow, OpenCV library, GraphQL} \\
    }}
 \end{itemize}
 \vspace{-16pt}


\section{Publications}
 \begin{itemize}
\small{ 
\item Patel N., Shinde S., Poly F., "Automated Damage Detection in Operational Vehicles Using Mask R-CNN". \textit{Advanced Computing Technologies and Applications. Algorithms for Intelligent Systems. Springer, Singapore 2020, } pp. 563-571 
\item A. Srivastava, S. Shinde, N. Patel, S. Despande, A. Dalvi and S. Tripathi, ”Questionator-Automated Question Generation using Deep Learning,” \textit{2020 International Conference on Emerging Trends in Information Technology and Engineering (ic-ETITE), 2020},  pp. 1-5
\item N. Patel, Y. Singh, S. Reddy, “FaceCognize : An approach to Face Recognition for low resolution images” \textit{2021 Asian Conference on Innovation in Technology, Pune(\textbf{Accepted and presented})}
\item S Patel., N. Patel, S Deshpande, A. Siddhique Ship Intrusion Detection using Custom Object Detection System with YOLO Algorithm. \textit{International Research Journal of Engineering \& Technology. 2021, Volume 8 Issue 1}  
}

\end{itemize}

 
 


%-----------INVOLVEMENT---------------
\section{Extracurricular}
\begin{itemize}
\small{
    \item Helped start the first ever \textbf{AI and DL Club (FCRIT-AID)} in association with Benitt University and was elected as \textbf{Chairman} during the 2018-2019. Organized numerous seminars and workshop on topics ranging from RPA, Data science, Deep learning, big data.  

    \item Won the \textbf{1st prize} in the \textbf{IEEE Technical presentation award 2019} held by the \textbf{FCRIT IEEE chapter} for the paper - "Questionator.ai - automated question generation". 

    \item Qualified as \textbf{one} of the \textbf{5 teams} winning at the \textbf{Internal Smart India hackathon 2020} and selected to represent at SIH 2020 for the project titled - “capture face, expression, gesture of Targeted persons through distributed CCTV”. 

    \item Partnered with local teachers to tutor underprivileged children in Mathematics and Science as part of Seva Sahyog Foundation in year.  

    \item Part of the \textbf{Computer society of India (CSI)} where I took part in numerous workshops and competitions that were organized. 
    
}

\end{itemize}


\end{document}
